EinsteinPy: A Community Python Package for General Relativity

### 2020-05-18 paper_two.tex
Add a refree version and a print version

%
\documentclass[onecolumn]{aa}  
%\documentclass[bibyear]{aa}
%\documentclass[onecolumn]{aa}  
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{url}
\usepackage[xindy, toc, hyperfirst=false, nolist, nostyles, sanitize={name=false,description=false,symbol=false}]{glossaries}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\begin{document}

@@

Pratyush Kerhalkar\inst{\ref{inst:elecmani}}

@@

Shamanth R Nayak K\inst{\ref{inst:manipalit}}

@@

Vineet Gandham\inst{\ref{inst:manipalcs}}

@@

Atul Mangat\inst{\ref{inst:iitree}}

@@

Suyash Salampuria\inst{\ref{inst:iitrce}}

@@

Gagan Shenoy\inst{\ref{inst:manipalcs}}

@@

  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005

@@

  Department of Earth Sciences, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India

@@

   Department of Electronics and Communication Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   Department of Computer Engineering, Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India

@@

   Department of Information and Communication Technology Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   \label{inst:manipalit}
   Department of Computer Science and Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   \label{inst:manipalcs}

@@

  Department of Electrical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
  \label{inst:iitree}
  Indian Institute of Information Technology, Design and Manufacturing, Kancheepuram, Off Vandalur-Kelambakkam Road, Melakottaiyur, Chennai, Tamil Nadu, India 600127

@@

  Department of Chemical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
  \label{inst:iitrce}

@@

  \abstract
{This paper presents EinsteinPy (version 0.3), a community-developed Python package for gravitational and relativistic astrophysics. Python is a free, easy to use a high-level programming language which has seen a huge expansion in the number of its users and developers in recent years. Specifically, a lot of recent studies show that the use of Python in Astrophysics and general physics has increased exponentially. Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interface and pleasing user experience. One such example is Keras - a framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier. This example demonstrates the power of abstraction which is achievable in Python. The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research. Currently, EinsteinPy supports simulation of time-like and null geodesics and calculates trajectories in different background geometries some of which are Schwarzschild, Kerr, and KerrNewmann along with coordinate inter-conversion pipeline. It has a partially developed pipeline for plotting and visualization with dependencies on libraries like Plotly, matplotlib, etc. One of the unique features of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilities which are a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky. EinsteinPy also provides few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation. The current version of the library is in a state that can be used by any serious student of general relativity trying to get the essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject. EinsteinPy provides such students to really see through the equations and visualize what's really happening.}

>>>>

%
\documentclass[refree]{aa}  
%\documentclass[bibyear]{aa}
%\documentclass[onecolumn]{aa}  
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{url}
\usepackage[xindy, toc, hyperfirst=false, nolist, nostyles, sanitize={name=false,description=false,symbol=false}]{glossaries}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\begin{document}

@@

Pratyush Kerhalkar\inst{\ref{inst:manipal}}

@@

Shamanth R Nayak K\inst{\ref{inst:manipal}}

@@

Vineet Gandham\inst{\ref{inst:manipal}}

@@

Atul Mangat\inst{\ref{inst:iitr}}

@@

Suyash Salampuria\inst{\ref{inst:iitr}}

@@

Gagan Shenoy\inst{\ref{inst:manipal}}

@@

  Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005

@@

  Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India

@@

   Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India

@@

   Manipal Institute of Technology, Manipal, Karnataka, India

@@

  Indian Institute of Information Technology, Design and Manufacturing, Chennai, Tamil Nadu, India 600127

@@

@@

  \abstract
{This paper presents EinsteinPy (version 0.3), a community-developed Python package for gravitational and relativistic astrophysics. Python is a free, easy to use a high-level programming language which has seen a huge expansion in the number of its users and developers in recent years. Specifically, a lot of recent studies show that the use of Python in Astrophysics and general physics has increased exponentially. We aim to provide a very high level of abstraction, an easy to use interface and pleasing user experience. EinsteinPy is developed keeping in mind the state of a theoretical gravitational physicist with little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research. Currently, EinsteinPy supports simulation of time-like and null geodesics and calculates trajectories in different background geometries some of which are Schwarzschild, Kerr, and KerrNewmann along with coordinate inter-conversion pipeline. It has a partially developed pipeline for plotting and visualization with dependencies on libraries like Plotly, matplotlib, etc. One of the unique features of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilities which are a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky. EinsteinPy also provides few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.}
